
---
output:
  distill::distill_article:
    self_contained: false
    lib_dir: libs
description: MINNEAPOLIS, MN 
date: 12-10-2020
title: ADAMS COMMUNICATIONS COMPANY 
---




```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(feather)
library(knitr)
library(dplyr)
library(kableExtra)

db <- read_feather('../ppp builder-PRIVATE/inter/ppp.top.10k.feather')

```



The **Paycheck Protection Program (PPP)** was designed to provide a direct incentive for small businesses to keep their workers on the payroll. It ended in August 2020, but a [new PPP bill](https://thehill.com/policy/finance/529092-bipartisan-support-for-new-ppp-loans-gains-momentum-in-congress) is being considered.

As part of the Paycheck Protection Program **ADAMS COMMUNICATIONS COMPANY, LLC** received a loan.


# ADAMS COMMUNICATIONS COMPANY, LLC 

```{r}
focal.row <- db[db$id ==  119715 , ]
focal.row$id <- NULL
focal.row$LoanAmount <- NULL
focal.row$BusinessName.hyphenated <- NULL

knitr::kable(t(focal.row), 
col.names = '') %>%
kable_styling(latex_options = 'striped') %>%
  column_spec(1, bold = TRUE)


```

### Data Sources

The data come from a release of over 5,000,000 records by the SBA in November, 2020.


### Who Could Apply?

The following entities affected by Coronavirus (COVID-19) may have been eligible:

+ Any small business concern that meets SBA’s size standards (either the industry based sized standard or the alternative size standard)
+ Sole proprietors, independent contractors, and self-employed persons
+ Any business with a NAICS Code that begins with 72 (Accommodations and Food Services) that has more than one physical location and employs less than 500 per location
+ Any business, 501(c)(3) non-profit organization, 501(c)(19) veterans organization, or Tribal business concern (sec. 31(b)(2)(C) of the Small Business Act) with the greater of:
  + 500 employees, or 
  + That meets the SBA industry size standard if more than 500


More info about the PPP is available from the [Small Business Administration](https://www.sba.gov/funding-programs/loans/coronavirus-relief-options/paycheck-protection-program).

 
### Other companies that received a PPP loan 
   
 [ADVANCE CARE ALLIANCE OF NY](/Paycheck-Protection-Program/-130241-ADVANCE-CARE-ALLIANCE-OF-NY/) <br> [ADVANCED CALL CENTER TECHNOLOGIES](/Paycheck-Protection-Program/-132298-ADVANCED-CALL-CENTER-TECHNOLOGIES/) <br> [ADVANCED CLINICAL HOLDINGS](/Paycheck-Protection-Program/-132718-ADVANCED-CLINICAL-HOLDINGS/) <br> [ADVANTAGE CONSULTING AND EDUCATIONAL SERVICES](/Paycheck-Protection-Program/-139818-ADVANTAGE-CONSULTING-AND-EDUCATIONAL-SERVICES/) <br>